Comprehensive Quality Awareness Automated Semantic Web Service Composition

### 2017-03-30 paper.tex
update

QoS-aware web service composition is studied using traditional approaches or Evolutionary Computation (EC) techniques for finding near-optimised solutions. Qi et al. \cite{qi2010combining} propose a heuristic service composition method, named LOEM (Local Optimisation and Enumeration Method), where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near optimal QoS. EC techniques are used to automatically generate solutions with optimal QoS. Gupta et al. \cite{gupta2015optimization} employ a modified Genetic Algorithm (GA) using a binary string as an individual, which demands to be decoded into composition solutions. Genetic Programming (GP) are used by Yu et al. \cite{yu2013adaptive}, the optimal solutions are reached by penalising infeasible solutions using a fitness function. A hybrid approach employing a greedy search and GP is introduced in \cite{ma2015hybrid} to generate functionally correct tree-based individuals, which are transformed from DAGs. To eliminating the transformation process, a promising GraphEvol is proposed in \cite{da2015graphevol}, where DAG-based service composition representations employ Graph-based evolutionary operators. An indirect PSO-based approach was introduced in \cite{da2016particle}. An optimised queue is used as an indirect representation that is decoded into a DAG. These QoS-aware approaches \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive} do not consider semantic matchmaking quality, which could lead to too specific outputs produced by the selected services.

@@

The first column of Table \ref{meanFitness} shows five tasks from WSC09 Dataset. The second and third column of Table \ref{meanFitness} show the orginal service repository size before the greedy search and shrunk service repository size after the greedy search respectively regarding the five tasks. This greedy search helps reducing the repository size by considering only task-related service candidates, which also contributes to a significant reduced researching space. The fourth and fifth column of Table \ref{meanFitness} show the mean fitness values of 30 independent runs accomplished by two methods. We employ independent-samples T tests to test the significant differences in mean fitness value. The results show that the PSO-based approach outperformes the existing GP-based approach in most cases except task 3 (all the p-values are consistently smaller than 0.01). In task 5, PSO-based approach performs significantly better than GP-based approach in finding optimal solutions. It may refer to that GP-based approach is stuck in the local optimal due to a very large searching space in Task 5, but PSO-based approach requres decoding processes of sorted queues, where small changes of the queues might lead to different decoded solutions.

\begin{table}[]
\centering
\caption{Mean fitness results for comparing GP-based approach}
\label{meanFitness}
\begin{tabular}{c|c|c|l|l}
\hline
\multicolumn{1}{c|}{WSC09} &Original $SR$  &Shrunken $SR$   &PSO-based approach & GP-based approach  \\ \hline
Task 1                     &572            &80    &0.5592 $\pm$ 0.0128  $\uparrow$  &0.5207 $\pm$ 0.0208           \\ \hline
Task 2                     &4129           &140   &0.4701 $\pm$ 0.0011  $\uparrow$  &0.4597 $\pm$ 0.0029          \\ \hline
Task 3                     &8138           &153   &0.5504 $\pm$ 0.0128              &0.5679 $\pm$ 0.0234 $\uparrow$   \\ \hline
Task 4                     &8301           &330   &0.4690 $\pm$ 0.0017  $\uparrow$  &0.4317 $\pm$ 0.0097            \\ \hline
Task 5                     &15211          &237   &0.4694 $\pm$ 0.0008  $\uparrow$  &0.2452 $\pm$ 0.0369            \\ \hline
\end{tabular}
\end{table}

>>>>

QoS-aware web service composition is studied using traditional approaches or Evolutionary Computation (EC) techniques for finding near-optimised solutions. Qi et al. \cite{qi2010combining} propose a heuristic service composition method, named LOEM (Local Optimisation and Enumeration Method), where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near optimal QoS. EC techniques are used to automatically generate solutions with optimal QoS. Gupta et al. \cite{gupta2015optimization} employ a modified Genetic Algorithm (GA) using a binary string as an individual, which demands to be decoded into composition solutions. Genetic Programming (GP) are used by Yu et al. \cite{yu2013adaptive}, the optimal solutions are reached by penalising infeasible solutions using a fitness function. A hybrid approach employing a greedy search and GP is introduced in \cite{ma2015hybrid} to generate functionally correct tree-based individuals, which are transformed from DAGs. To eliminating the transformation process, a promising GraphEvol is proposed in \cite{da2015graphevol}, where DAG-based service composition representations employ Graph-based evolutionary operators. An indirect PSO-based approach was introduced in \cite{da2016particle}. An optimised queue is used as an indirect representation that is decoded into a DAG. These QoS-aware approaches \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive} do not consider semantic matchmaking quality.

@@

The first column of Table \ref{meanFitness} shows five tasks from WSC09 Dataset. The second and third column of Table \ref{meanFitness} show the orginal service repository size before the greedy search and shrunk service repository size after the greedy search respectively regarding the five tasks. This greedy search helps reducing the repository size by considering only task-related service candidates, which also contributes to a significant reduced researching space. The fourth and fifth column of Table \ref{meanFitness} show the mean fitness values of 30 independent runs accomplished by two methods. We employ independent-samples T tests to test the significant differences in mean fitness value. The results show that the PSO-based approach outperformes the existing GP-based approach in most cases except task 3 (all the p-values are consistently smaller than 0.01). In task 5, the PSO-based approach performs significantly better than the GP-based approach in finding optimal solutions. It may be that the GP-based approach is stuck in local optima due to the very large search space in Task 5. On the other hand, the decoding process used by the PSO-based approach allows for small changes that more effectively prevent this from happening.
\begin{table}[]
\centering
\caption{Mean fitness results for comparing GP-based approach}
\label{meanFitness}
\begin{tabular}{c|c|c|l|l}
\hline
\multicolumn{1}{c|}{WSC09} &Original $SR$  &Shrunken $SR$   &PSO-based approach & GP-based approach  \\ \hline
Task 1                     &572            &80    &0.5592 $\pm$ 0.0128  $\uparrow$  &0.5207 $\pm$ 0.0208           \\ \hline
Task 2                     &4129           &140   &0.4701 $\pm$ 0.0011  $\uparrow$  &0.4597 $\pm$ 0.0029          \\ \hline
Task 3                     &8138           &153   &0.5504 $\pm$ 0.0128              &0.5679 $\pm$ 0.0234 $\uparrow$   \\ \hline
Task 4                     &8301           &330   &0.4690 $\pm$ 0.0017  $\uparrow$  &0.4317 $\pm$ 0.0097            \\ \hline
Task 5                     &15211          &237   &0.4694 $\pm$ 0.0008  $\uparrow$  &0.2452 $\pm$ 0.0369            \\ \hline
\end{tabular}
\end{table}
